---
title: "Alcohol vs Seat choice"
author: "Amia Little"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you sit in?

The data came from UCDavis in the year...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.




# Methods 
In the data set davisdata seat is a categorical variable, alcohol is numerical   

We try to predict alcohol based ~ Seat. So we use the Numerical ~ Cat.rmd helper file.

# Results

## Descriptive results

### Graphical summary
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
This boxplot shows that your consumption of alcohol has almost 0 effect on where you sit in the class...



### Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The Numerical summary shows that alcohol consumption has very little effect on where you sit in class. 




### Inferential results






```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.0000116 less than 0.05 so we reject the null hypothesis. 
There is a difference in alcohol consumption based on where people sit in class.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
The turkeyhsd model shows the differences in seating levels 
The difference in seating levels is 5.


## Conclusions 

In the data set davisdata seat is a categorical variable, alcohol is numerical.
We used Numerical ~ Cat helper file to predict alcohol ~ seat
P-value is 0.0000116 less than 0.05 so we reject the null hypothesis.
There is a difference in alcohol consumption based on where people sit in class.
The average number drinks is different between at least two rows.      






